ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python

### 2016-08-27 doc/paper.tex
writing & editing more

\pagestyle{fancy}

@@

@@

Use of ScPy is through two UGens: \texttt{Py} and \texttt{PyOnce}. Both have one required argument,
a block of Python code. A map of variable names may optionally be provided to bind SuperCollider
variables to Python variables.  Additionally, there is an optional \texttt{DoneAction} argument which
specifies an action to occur in SuperCollider after the Python code has finished executing.

@@

def fn(x):
    x = pv.forward(x)
    idx = indices(x.shape)[1]
    x = pv.shift(x, lambda freq:
        freq * (0.8 + mod(-time + 0.1*idx, 10)*0.045))
    x = pv.backward(x)
    return x
    \end{minted}
    \caption{A novel effect to transform any sound into a falling Shepard tone. This example makes
    use of the phase vocoder \texttt{shift} operation, which applies a function to frequency, then
    reorganizes the spectrum to move the new frequencies into the appropraite bins.}
    \label{lst:shepard}
\end{listing}

@@

As shown in \autoref{lst:shepard} and \autoref{lst:binflipper}, ScPy includes a phase vocoder
implemented in Python for performing frequency transformations. Interestingly, although all of
SuperCollider's FFT operations are referred to as phase vocoder operation, there is actually no
implementation of a phase vocoder to be found in SuperCollider at the time of writing. It is likely
that a phase vocoder was once intended to be implemented, but the 32 so-called phase vocoder
effects are simply transformations to the cartesian or polar representations of the spectrum.

@@

Support for more SuperCollider types, such as events or strings could additionally be added.

@@

\section{Conclusion}

>>>>

\pagestyle{fancy}
\lhead{\leftmark}
\chead{}
\rhead{}

@@

ScPy is developed and maintained as an open-source project under the GPLv3 license. The
latest code and documentation is available on GitHub\footnote{\url{https://github.com/nwoeanhinnogaehr/ScPy}}.

@@

Use of ScPy is through the classes \texttt{Py} and \texttt{PyOnce}. \texttt{Py} is used for
processing real-time data, and \texttt{PyOnce} is used for doing initialization or other one time
processing. Both have one required argument, a block of Python code. A map of variable names may
optionally be provided to bind SuperCollider variables to Python variables.  Additionally, there is
an optional \texttt{DoneAction} argument which specifies an action to occur in SuperCollider after
the Python code has finished executing.

@@

def fn(x):
    x = pv.forward(x)
    idx = indices(x.shape)[1]
    x = pv.shift(x, lambda freq:
        freq * (0.8 + mod(-time + 0.1*idx, 10)*0.045))
    x = pv.backward(x)
    return x
    \end{minted}
    \caption{A novel effect to transform any sound into a falling Shepard tone. This example makes
    use of the phase vocoder \texttt{shift} operation, which applies a function to frequency, then
    reorganizes the spectrum to move the new frequencies into the appropriate bins.}
    \label{lst:shepard}
\end{listing}

@@

As shown in \autoref{lst:shepard} and \autoref{lst:binflipper}, ScPy includes a phase vocoder
implemented in Python for performing frequency transformations. Interestingly, although all of
SuperCollider's FFT operations are referred to as phase vocoder operations, there is actually no
implementation of a phase vocoder to be found in the SuperCollider code base at the time of
writing. It is likely that a phase vocoder was once intended to be implemented, but the 32
so-called phase vocoder effects are simply transformations to the Cartesian or polar
representations of the spectrum.

@@

Support for more SuperCollider types, such as events or strings, could be added to open up ScPy to
more use cases.

Multi-core processing support would allow for many more sounds to be processed in real-time.

@@

Although extending SuperCollider was the focus of this project, similar improvements could be made
to the CSound\cite{boulanger2000csound,lazzarini2005extensions}, Chuck\cite{wang2008chuck} or
Faust\cite{orlarey2009faust} environments as well.
